\documentclass{article}
\usepackage{multirow}
\usepackage{booktabs}

\title{MCR3U Functions University Course}
\author{Kensukeken}
\date{January 30, 2023}

\begin{document}

\maketitle

\section{Introduction}
The MCR3U (Grade 11 Functions) course is a foundational mathematics course offered at the university level. It is designed to provide students with a comprehensive understanding of functions, equations, and their applications in various fields such as engineering, science, and economics.

\section{Course Content}
The course covers a wide range of topics including:
\begin{itemize}
    \item Prerequisite Review of Concepts
    \item Introduction to Functions
    \item Algebraic Expressions
    \item Quadratic Functions
    \item Exponential Functions
    \item Functions \& Applications of Trigonometry
    \item Discrete Functions
\end{itemize}

\section{Course Objectives}
The main objectives of the MCR3U course are to:
\begin{itemize}
    \item Develop students' ability to analyze and interpret mathematical models.
    \item Enhance problem-solving skills through the application of mathematical concepts.
    \item Prepare students for further studies in mathematics and related fields at the university level.
\end{itemize}

\section{Assessment}
Assessment in the MCR3U course may include quizzes, tests, assignments, projects, and a final exam. These assessments are designed to evaluate students' understanding of course material and their ability to apply mathematical concepts to real-world problems.

\section{Conclusion}
The MCR3U course provides students with a solid foundation in functions and equations, equipping them with the necessary skills and knowledge to succeed in higher-level mathematics courses and pursue various academic and career paths.

\begin{table}[h]
\centering
\begin{tabular}{@{}ccc@{}}
\toprule
\textbf{Unit Order} & \textbf{Unit Name} & \textbf{Suggested Time (Hours)} \\ \midrule
0 & Prerequisite Review of Concepts & 5 \\
 & Introduction to Functions & 15 \\ \midrule
1 & Algebraic Expressions & 13 \\
 & Quadratic Functions & 20 \\ \midrule
\multirow{2}{*}{\textbf{MID SEMESTER POINT}} & Exponential Functions & 15 \\
 & Functions \& Applications of Trig & 25 \\ \midrule
2 & Discrete Functions & 15 \\
 & Final Exam & 2 \\ \midrule
\multicolumn{2}{r}{\textbf{Total}} & \textbf{110} \\ \bottomrule
\end{tabular}
\caption{Unit Order and Suggested Time}
\label{tab:unit_order}
\end{table}

\end{document}
